How to compute the fusion product of MV cycles in type A

### 2021-04-12 draft.tex
added min weights and tableaux

    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]\,. 
    \]
    % 
     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    For example,
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]\,. 
    \]
    % For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]
    % 
    % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
    % \acom{Ok.}
    % 
    \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
    $$
    \end{definition}
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).

    Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices. For example, elements of $ \UU_{0,s}^{(1,1,0),(2,1,1)}$ look like 
% 
% $\UU_{0,0}^{(?),(?)}$ entries look like 
% \[
%     \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
%         0 & 1 & 0 & 0 & 0\\
%         0 & 0 & 1 & 0 & 0\\
%         0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
%         0 & 0 & 0 & 0 & 1\\
%         0 & 0 & 0 & 0 & 0
%         \end{BMAT}\right]    
%         % \mapsto 
%         % \left[\begin{array}{rr}
%         %     t^{3} & 0 \\
%         %     -A_{12}^2 t - A_{12}^1 & t^{2}
%         % \end{array}\right]
% \]
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right] \,.    % \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]

@@

Computing fusion still hard but at least boiled down to linear algebra. Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,Mirkovi\'c2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.

@@

\section{Denouement}
\label{s:denouement}

As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$. Well yeah.

\begin{proposition}(\cite{baumann2019Mirkovi\'c})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''\in P_{++}$ and weight $\mu',\mu''\in P$ resp.\ such that $\mu = \mu' + \mu'' \in P_{++}$. Then 
    \begin{equation}
        % Z_\tau\ast Z_\sigma 
        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        = 
        % \sum_{Z\in\cZ(\lambda)_\mu} 
        \sum_{\tau\in S(\lambda)_\mu}
        i\left(
            Z_\tau, Z'\circ Z''
            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
        \right) [Z_\tau]
    \end{equation}
    and the intersection multiplicities on the right are found by the algorithm described in APX.
    In particular, 
    the multiplicity of $Z_\tau$
    % in the product of the zero fiber 
    % (divisor class) 
    % and the 
    % (Zariski) 
    % closure of the family $Z_1 \times Z_2 \times U$ 
    is equal to the multiplicity of its generalized orbital variety $X_\tau$ among the set 
    \begin{equation}\label{eq:tabmult}
        \irr\lim_{s\to 0} \overline{\OO}^{\lambda',\lambda''}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
    \end{equation}
    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z' \circ Z''
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$.
\end{proposition}
\acom{or Corollary?}

\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
    Then 
    \begin{equation}
        i(\tau, 
        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
        % Z_1 \circ Z_2 
        \tau' \circ \tau''
        ) = 1 \,. 
    \end{equation}
\end{conjecture}

\begin{proposition}
    Given Lusztig data $n_\bullet',n_\bullet''\in\NN^\ell$ the smallest choice of $\mu',\mu''\in P$ and $\lambda',\lambda''\in P_{++}$ such that $\mu = \mu' + \mu''\in P_{++}$ and $\tau'\in S(\lambda')_{\mu'}$, $\tau''\in S(\lambda'')_{\mu''}$ are SSYT with the prescribed Lusztig data, are\dots
\end{proposition}
\begin{proof}
    [Sketch.]
    The last row of the GT pattern of $\tau'$ (resp.\ $\tau''$) is $\lambda'$ (resp.\ $\lambda''$). 
    Guess: the smallest choices will be the appropriate pieces of the smallest choices for $\lambda$, $\mu$, and $n_\bullet = n_\bullet' + n_\bullet''$. E.g.\ take $n_\bullet' = (2,0,0), n_\bullet'' = (0,0,2)$ so $n_\bullet = (2,0,2)$. Then $\lambda - \mu = 2\alpha_1 + 2\alpha_2$ %or $(\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,2)$ 
    \begin{gather}
        (\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,-2)
        \\
        % (\lambda_1(2) - \mu_1(2),\lambda_2(2) - \mu_2(2), \lambda_3(2) - \mu_3(2)) &= (2,0,2) \\
        % (\lambda_1(1) - \mu_1(1),\lambda_2(1) - \mu_2(1), \lambda_3(1) - \mu_3(1)) &= (2,0,2)
        \begin{matrix}
            & & \lambda_1(1) \\
            & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
            \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & \lambda_3 
        \end{matrix}\\
        \Rightarrow \mu_3 \ge 2, \mu_2 \ge 2, \mu_1 \ge 2 \\
        \Rightarrow \lambda_3 \ge 0, \lambda_2 \ge 2, \lambda_1 \ge 4 \\
        \Rightarrow \lambda_2(2) = \lambda_2 - 2 \ge 0 , \lambda_1(2) = \lambda_1 \ge 4 \\ 
        \Rightarrow \lambda_1(1) = \lambda_1(2) - 2 \ge 2 \\ 
        \young(1122,33)
        % \Leftrightarrow 
        % \begin{matrix}
        %     & & \lambda_1(1) \\
        %     & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
        %     \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & 0 
        % \end{matrix}
    \end{gather} 
    Since the tableau formed by taking the smallest possible choices for each of the inequalities is semi-standard we're good.

    In general we have $\mu_i\ge\sum_k n_{i,k}$ where $n_{i,k} = \lambda_k(i) - \lambda_{k}(i-1)$ and then $\lambda_i \ge \nu_i + \mu_i$ where $\nu = \wt(n_\bullet)$. The rest of the lower bounds are determined recursively by the relation $\lambda_k(i-1) =  \lambda_k(i) - n_{i,k}$. Choose the minimum values satisfying the bounds until $\lambda_k(i) < \lambda_{k+1}(i)$ for some $k,i$. If this should happen go back to the start and increment all/some of the initial $\lambda_k$ by an appropriate amount.
\end{proof}

% TODO: un-appendicize 
% \appendix

\subsection{Generalized orbital varieties?}
TODO: recall $\tau\mapsto X_\tau \mapsto Z_\tau$

\subsection{Pseudocode}

\begin{question}
    Smallest $\mu_1, \mu_2$ such that\dots?
\end{question}

\subsection{Tableaux and families}

TODO: $Z_1\ast_\AA Z_2$ is described by $\tau_1\ast\tau_2$ or $\tau_1\sqcup\tau_2$

>>>>

    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]\,. 
    \]
     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    For example,
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]\,. 
    \]
    % For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]
    % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
    % \acom{Ok.}
    \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
    For example, elements of $ \UU_{0,s}^{(1,1,0),(2,1,1)}$ look like 
% $\UU_{0,0}^{(?),(?)}$ entries look like 
% \[
%     \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
%         0 & 1 & 0 & 0 & 0\\
%         0 & 0 & 1 & 0 & 0\\
%         0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
%         0 & 0 & 0 & 0 & 1\\
%         0 & 0 & 0 & 0 & 0
%         \end{BMAT}\right]    
%         % \mapsto 
%         % \left[\begin{array}{rr}
%         %     t^{3} & 0 \\
%         %     -A_{12}^2 t - A_{12}^1 & t^{2}
%         % \end{array}\right]
% \]
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right] \,.    % \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]
    Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.

    \acom{Mention that any other decomposition $\nu' + \nu''$ of $\mu' + \mu''$ will give a slice $\UU^{\nu',\nu''}_{0,\AA}$ with the same zero fibre.}

@@

Computing fusion still hard but at least boiled down to linear algebra. Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.

@@

\section{Denouement}
\label{s:denouement}
% 
In this section we demonstrate how to put the main results of this paper into practice.
% 
Given $\lambda$ dominant effective and $\mu\le\lambda$ effective, let $YT(\lambda)_\mu$ denote the set of semistandard Young tableaux of shape $\lambda$ and weight $\mu$. 
%

We need the following result from \cite{dthesis}.
\begin{proposition}
    Generalized orbital varieties are indexed by semistandard Young tableaux. Composing with the ordinary Mirkovi\'c--Vybornov isomorphism gives bijections 
    \[
        YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \irr \overline\Gr^\lambda\cap S^\mu_-\,. 
    \]
    % $$
    % \begin{tikzcd}
    %     YT(\lambda)_\mu \ar[r] \ar[d] & \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \ar[d] \\
    %     GT(\lambda)_\mu \ar[r] & \irr \overline\Gr^\lambda\cap S^\mu_-
    % \end{tikzcd}
    % $$
\end{proposition}
% 
Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. 
% 
\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of coweight $(\lambda',\mu'),(\lambda'',\mu'')$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
    Then 
    \begin{equation}
        \label{eq:tabmult}
        % Z_\tau\ast Z_\sigma 
        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        = 
        % \sum_{Z\in\cZ(\lambda)_\mu} 
        \sum_{\tau\in S(\lambda)_\mu}
        i\left(
            Z(\tau), Z'\circ Z''
            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
        \right) [Z(\tau)]
    \end{equation}
    and the intersection multiplicities on the right are found by the algorithm described in \Cref{ss:algo}.

    \acom{Add pseudocode}

    In particular, the multiplicity of $Z(\tau)$
    % in the product of the zero fiber 
    % (divisor class) 
    % and the 
    % (Zariski) 
    % closure of the family $Z_1 \times Z_2 \times U$ 
    is equal to the multiplicity of its generalized orbital variety $X(\tau)$ 
    in $ \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} $. 
    % among the set 
    % \begin{equation}\label{eq:tabmult}
        % \irr\lim_{s\to 0} 
        % \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} \,. 
        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
    % \end{equation}

    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z' \circ Z''
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \Cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$. These are described in \Cref{lem:mintab,prop:minwts} below.
\end{proposition}
% 
\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
    Then 
    \begin{equation}
        i(\tau, 
        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
        % Z_1 \circ Z_2 
        \tau' \circ \tau''
        ) = 1 \,. 
    \end{equation}
\end{conjecture}
%

\begin{lemma}
    \label{lem:mintab}
    Let $n_\bullet$ be a Lusztig datum of coweight $\nu$. There exist $\lambda,\mu$ smallest such that $n_\bullet$ is the Lusztig datum of a tableau $\tau\in YT(\lambda)_\mu$. They are determined by the following minimization problem. Regard $n_\bullet$ as a strictly lower triangular matrix with $(r,c)$th entry $n_{r,c}$ is equal to the number of boxes of weight $r$ in row $c$ of $\tau$. Note that since $r > c$ this data does not account for the number of boxes of weight $r$ in row $r$. Let $\mu^0$ be the diagonal matrix whose $(r,r)$th entry $\mu^0_r$ is equal to the number of boxes of weight $r$ in row $r$ of $\tau$. Note that the sum of the rows of $n_\bullet + \mu^0$ is the shape $\lambda$ of $\tau$, and the sum of the columns of $n_\bullet + \mu^0$ is the weight $\mu$ of $\tau$. The solution to the minimization problem 
    \[
        \begin{gathered}
        % 
        \text{minimize }\mu^0\text{ such that} \\
        % \text{the sum of the rows of }n_\bullet + \mu^0\text{ is non-increasing},
        % \text{the sum of the columns of }n_\bullet + \mu^0\text{ is non-increasing}
        \text{both }\lambda,\mu\text{ are non-increasing}
        \end{gathered} 
    \]
    is got recursively from % setting $\mu^0_m = 0$, 
    \[
        \begin{gathered}
            \mu^0_{m} = 0 \\ 
            \mu^0_{m-1} = \max\{0 , \sum n_{m,c} - \sum n_{m-1,c}\} \\ 
            \mu^0_i = \max\{0, \mu^0_{i+1} + \sum n_{i+1,c} - \sum n_{i,c} , \mu_{i+1}^0 + \sum n_{r,i+1} - \sum n_{r,i}\}
        \end{gathered}
    \]
    for $i = 1,\dots,m-2$. 
    In words, given a Luszig datum $n_\bullet$, if we wish to produce a minimal SSYT for it, 
    \begin{itemize}
        \item we can always take the number of $m$'s in row $m$ to be zero; 
        \item we can take the number of $m-1$'s in row $m-1$ to be zero, unless $n_\bullet$ tells us that there are more $m$'s the first $m-1$ rows than there are $m-1$'s in the first $m-2$ rows, and in that case we take $\mu^0_{m-1}$ so that it exactly offsets the difference; 
        \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us there are more $m-1$'s in the first $m-1$ rows (building off the last step) than there are $m-2$'s in the first $m-3$ rows, or, that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the minimum of the two differences; 
        \item induct up to $\mu^0_1$. 
    \end{itemize}
\end{lemma}

\begin{proposition}
    \label{prop:minwts}
    Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest choice of effective coweights $\mu',\mu''$ and effective dominant coweights $\lambda',\lambda''$ such that $\mu = \mu' + \mu''$ is effective dominant and $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ are semistandard Young tableaux with the prescribed Lusztig data. They are got by choosing the minimum $\lambda,\mu$ for $n_\bullet = n_\bullet ' + n_\bullet ''$ afforded by \Cref{lem:mintab}, and then breaking off $n_{r,c}'$ boxes of weight $r$ from each row $c<r$ of $\tau$ to form a $\tau'_0$ an intermediate tableau. If $\tau'_0$ is of an acceptable shape then we keep it. If it is not, then we correct it by padding it using some boxes of weight $r$ in row $r$ of what remains of $\tau$.

    \acom{To be completed.}
\end{proposition}

\subsection{Pseudocode}
%

\subsection{Tableaux and families}
% 
TODO: resume here

$Z'\ast_\AA Z''$ is described by $\tau'\ast\tau''$
